Research Plan for Multi-Agent Path Finding with matching using Increasing Cost Tree Search

### 2021-05-25 docs/plan.tex
Added advanced pruning, speeded up hashing
Added handling of unsolvable matchings, worked on paper introduction
Made pruned child generation an option

\documentclass[a4paper,10pt,english]{article}
\usepackage[T1]{fontenc}
\usepackage{geometry}
\geometry{verbose,tmargin=3cm,bmargin=3cm,lmargin=3cm,rmargin=3cm}
\usepackage[backend=biber,style=ieee]{biblatex}
\addbibresource{sources.bib}
\usepackage{babel}

@@

	\paragraph{Week 3} \textbf{This week: first ACS session (7-5 8:45-10:45)}

@@

		\item[25-5 ] Aim to finish up evaluation of algorithms, in particular comparison with algorithms derived within peer group.

@@

	\printbibliography

\end{document}

>>>>

\documentclass[a4paper,10pt,english]{article}
\usepackage[T1]{fontenc}
\usepackage{geometry}
\geometry{verbose,tmargin=3cm,bmargin=3cm,lmargin=3cm,rmargin=3cm}
\usepackage[backend=biber,style=ieee]{biblatex}
\addbibresource{sources.bib}
\usepackage{babel}
\usepackage[normalem]{ulem}

@@

	\paragraph{Week 3} \textbf{This week: first ACS session (7-5 8:45-10:45), deadline for 300 word section for paper, the introduction (6-5 23:59)}

@@

		\item[25-5 ] \sout{Aim to finish up evaluation of algorithms, in particular comparison with algorithms derived within peer group.} Evaluate pruning extension, adapt code to be fully configurable in terms of both pruning mechanisms and corresponding child-generation rules.

@@

\newpage
	\printbibliography
\end{document}
